QPLIB: A Library of Quadratic Programming Instances

### 2018-08-08 AnswerToTheReferees2_second.tex

\rep{We would like to thank the AE for his/her positive opinion on the revision we performed of our manuscript. 
%\leo{Togliamo la spiegazione degli algoritmi e sostituiamola con una citazione di un book-tutorial-survey-introduction.}
}

\bigskip
\textbf{Main points:}

\begin{itemize}
\item 
{\it
[from referee, paraphrased] 8. Please try to find a more precise definition of asypmtotically complete algorithm to 
cite.
}

\rep{We think that a formal definition of this class of algorithms goes beyond the scope of the paper. We instead added a pointer to the subsection in which the class is presented.}

### 2018-08-08 methods.tex
Update methods.tex

  Solution methods for QP can be broadly organized in four categories \cite{neumaier}: \emph{incomplete}, \emph{asymptotically complete}, \emph{complete}, and \emph{rigorous}.
  \begin{itemize}
  \item \textit{Incomplete} methods are only able to identify solutions, often locally optimal according to a suitable notion, and may even fail to find one even when one exists; in particular, they are typically unable to determine that an instance has no solution.
  \item \textit{Asymptotically complete} methods can find a globally optimal solution with probability one in infinite time, but again they cannot prove that a given instance is infeasible.
  \item \textit{Complete} methods find an approximate globally optimal solution within a prescribed optimality tolerance within finite time, or prove that none such exists (but see \S\ref{s:complete} below); they are often referred to as \emph{exact} methods in the computational optimization community.
  \item \textit{Rigorous} methods find globally optimal solutions within given tolerances even in the presence of rounding errors, except for ``near-degenerate cases''. Since none of the solvers we are using can be classified as rigorous, we limit ourselves to declaring solvers complete.
  \end{itemize}

>>>>

  Solution methods for QP can be broadly organized in four categories \cite{neumaier}: \emph{incomplete}, \emph{asymptotically complete}, \emph{complete}, and \emph{rigorous}.
  \begin{itemize}
  \item \textit{Incomplete} methods are only able to identify solutions, often locally optimal according to a suitable notion, and may even fail to find one even when one exists; in particular, they are typically unable to determine that an instance has no solution.
  \item \textit{Asymptotically complete} methods can find a globally optimal solution with probability one in infinite time, but  they cannot prove that a given instance is infeasible \textcolor{green}{(see \S\ref{sss:asymc} below)}.
  \item \textit{Complete} methods find an approximate globally optimal solution within a prescribed optimality tolerance within finite time, or prove that none such exists (but see \S\ref{s:complete} below); they are often referred to as \emph{exact} methods in the computational optimization community.
  \item \textit{Rigorous} methods find globally optimal solutions within given tolerances even in the presence of rounding errors, except for ``near-degenerate cases''. Since none of the solvers we are using can be classified as rigorous, we limit ourselves to declaring solvers complete.
  \end{itemize}
